Model

### 2019-09-06 stats/model.Rmd
add model runs

```{r}
# load this for model parameters with so_slope (0:2)
#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int
#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and forced positive slope for semantic knowledge
#sem_know_model <- readRDS("../saves/sem_know_model_pos_slope.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and with random intercepts for subjects
#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_ind.rds")

# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int, forced positive slope for semantic knowledge and with random intercepts for subjects
sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_pos_slope_ind.rds")

@@

model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("alignment", "me_effect"),sep = ", ")%>%
  mutate(age = as.numeric(age),
         me_effect =str_remove(me_effect,"[)]"),
         me_effect =str_remove(me_effect,'"'),
         me_effect =as.numeric(str_remove(me_effect,'"')),
         alignment = str_remove(alignment,'c[(]'),
         alignment =str_remove(alignment,'"'),
         alignment =str_remove(alignment,'"'))

@@

@@

ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)

@@

@@

```
```{r}
ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

@@

```{r}
p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()
```

data_comb <- read_csv("../data/combination.csv") %>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
         source = "Data")

@@

```{r}
ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

@@

cor_plot_age <- ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

@@

```{r}
ggarrange(
plot_item_params,plotg_subj_sigma,
plot_global_params,plot_subject_params,
cor_plot_age, plot_global_sigma,
ncol = 2, nrow = 3, common.legend = T, widths = c(1.7,1))

ggsave("../graphs/overview_wide_slope_wide_sigma_pos_slope_ind.png", width = 12, height = 10, scale = 1.2)

@@

  var sampleItemParameters = function(itemName) { 
    return [itemName, {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: Math.pow(gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        }), 2)
      }]
  }

@@

    // comment out to save memory
    query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])

@@

display(row.alignment)

        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])

@@

comb_model_data <- bind_rows(
  me_model_data %>%
    distinct(age, prior) %>%
    mutate(alignment = "congruent"),
  me_model_data %>%
    distinct(age, prior) %>%
    mutate(prior = 1 - prior, 
         alignment = "incongruent")
)

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 10,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

# saveRDS(sem_know_model, "../saves/sem_know_model_save pred.rds")

@@

```{r}
comb_model_pred_agg <- model_pred%>%
  group_by(alignment,item,age)%>%
  summarise(mean = estimate_mode(me_effect),
            uci = hdi_upper(me_effect),
            lci = hdi_lower(me_effect))%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))

ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

>>>>

sem_know_model <- readRDS("../saves/sem_know_model_variant3_50k.rds")

@@

model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("na", "me_effect"),sep = ",")%>%
  select(-na)%>%
  mutate(age = as.numeric(age),
         me_effect =as.numeric(str_remove(me_effect,"[)]")))

@@

```
# Plotting model parameters

@@

#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)

@@

model_plot
```

@@

```{r}
ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

@@

```{r}
p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

p_comb_model
```

```{r}
data_comb <- read_csv("../data/combination.csv") %>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
         source = "Data")

@@

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

p_data_model
```

@@

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

@@

```{r}
ggarrange(
plot_item_params,
plot_global_params,
p_data_model, plot_global_sigma,
ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))

ggsave("../graphs/overview_variant_3_50k.png", width = 12, height = 4, scale = 1.2)

@@

  var sampleItemParameters = function(itemName) { 
    return [itemName, {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }]
  }

@@

    // comment out to save memory
  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])

@@

      //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])

@@

comb_model_data <- bind_rows(
  me_model_data %>%
    distinct(age, prior) %>%
    mutate(prior = 1 - prior, 
         alignment = "incongruent"),

   me_model_data %>%
    distinct(age, prior) %>%
    mutate(alignment = "congruent")
)

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 50000,
                        burn = 25000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 100)
)

@@

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_50k.rds")

model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("na", "me_effect"),sep = ",")%>%
  select(-na)%>%
  mutate(age = as.numeric(age),
         me_effect =as.numeric(str_remove(me_effect,"[)]")))

@@

```{r}
comb_model_pred_agg <- model_pred%>%
  group_by(Chain, alignment,item,age)%>%
  summarise(mean = estimate_mode(me_effect),
            uci = hdi_upper(me_effect),
            lci = hdi_lower(me_effect))%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         Chain = factor(Chain))

ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(Chain~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()+
  scale_fill_viridis_d()
